Titeln på avhandlingens språk

### 2023-02-03 publications/2022Ainur/demo.tex
fixing figs

\begin{figure}
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{publications/2022Ainur/figures/demo_workload_1}
        \caption{Workload 1: \acs{MNIST} image classifier}\label{paper:olguinmunoz2022ainur:fig:wkld:mnist}
    \end{subfigure}%
    \hfill%
%    \vspace{1em}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{publications/2022Ainur/figures/demo_workload_2}
        \caption{Workload 2: inverted pendulum \acs{NCS}}\label{paper:olguinmunoz2022ainur:fig:wkld:ncs}
    \end{subfigure}
    \caption{Demonstration workloads}\label{paper:olguinmunoz2022ainur:fig:wkld}
\end{figure}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2022Ainur/figures/demo_workload_1}
        \caption{Workload 1: \acs{MNIST} image classifier}\label{paper:olguinmunoz2022ainur:fig:wkld:mnist}
    \end{subfigure}%
    \hfill%
%    \vspace{1em}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2022Ainur/figures/demo_workload_2}
        \caption{Workload 2: inverted pendulum \acs{NCS}}\label{paper:olguinmunoz2022ainur:fig:wkld:ncs}
    \end{subfigure}
    \caption{Demonstration workloads}\label{paper:olguinmunoz2022ainur:fig:wkld}
\end{figure}

### 2023-02-03 publications/2022CLEAVE/experiments.tex
fixing figs

\begin{figure}[t]
    \centering
    \begin{subfigure}[h]{.5\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{publications/2022CLEAVE/plots/fixed_video_topple_frac}
        \caption{Toppled plants.}\label{paper:olguinmunoz2022cleave:fig:video:toppled}
    \end{subfigure}%
%    \hfill%
    \begin{subfigure}[h]{.5\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{publications/2022CLEAVE/plots/fixed_video_angle_rms}
        \caption{Angle \gls{RMS}.}\label{paper:olguinmunoz2022cleave:fig:video:rms}
    \end{subfigure}\\
    \begin{subfigure}[h]{.5\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{publications/2022CLEAVE/plots/fixed_video_drop_frac}
        \caption{Packet losses.}\label{paper:olguinmunoz2022cleave:fig:video:drop}
    \end{subfigure}%
%    \hfill%
    \begin{subfigure}[h]{.5\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{publications/2022CLEAVE/plots/fixed_video_rtt}
        \caption{\glspl{RTT}.}\label{paper:olguinmunoz2022cleave:fig:video:rtt}
    \end{subfigure}%
    \caption{
        Multi-loop, resource-constrained setup results.
        Error bars indicate \SI{95}{\percent} \glspl{CI} in all plots.
    }\label{paper:olguinmunoz2022cleave:fig:video:results}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \begin{subfigure}[h]{.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2022CLEAVE/plots/fixed_video_topple_frac}
        \caption{Toppled plants.}\label{paper:olguinmunoz2022cleave:fig:video:toppled}
    \end{subfigure}%
    \hfill%
    \begin{subfigure}[h]{.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2022CLEAVE/plots/fixed_video_angle_rms}
        \caption{Angle \gls{RMS}.}\label{paper:olguinmunoz2022cleave:fig:video:rms}
    \end{subfigure}\\
    \begin{subfigure}[h]{.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2022CLEAVE/plots/fixed_video_drop_frac}
        \caption{Packet losses.}\label{paper:olguinmunoz2022cleave:fig:video:drop}
    \end{subfigure}%
%    \hfill%
    \begin{subfigure}[h]{.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2022CLEAVE/plots/fixed_video_rtt}
        \caption{\glspl{RTT}.}\label{paper:olguinmunoz2022cleave:fig:video:rtt}
    \end{subfigure}%
    \caption{
        Multi-loop, resource-constrained setup results.
        Error bars indicate \SI{95}{\percent} \glspl{CI} in all plots.
    }\label{paper:olguinmunoz2022cleave:fig:video:results}
\end{figure}
